Follow-up Samples

### 2017-04-21 submission/manuscript.Rmd

---
title: ""
bibliography: reference.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: microbiome.csl
fontsize: 12pt
geometry: margin=1.0in
---

@@

**Figure 1: General Differences between Adenoma, Advanced Adenoma, and Carcinoma Groups After Treatment.*. A) A significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`). Solid black points represent the median value for each diagnosis group. B) NMDS of the pre- and post-treatment samples for the adenoma group. C) NMDS of the pre- and post-treatment samples for the advanced adenoma group. D) NMDS of the pre- and post-treatment samples for the carcinoma group.

>>>>

---
title: ''
csl: microbiome.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: reference.bib
---

@@

**Figure 1: General Differences between Adenoma, Advanced Adenoma, and Carcinoma Groups After Treatment.** A) A significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`). Solid black points represent the median value for each diagnosis group. B) NMDS of the pre- and post-treatment samples for the adenoma group. C) NMDS of the pre- and post-treatment samples for the advanced adenoma group. D) NMDS of the pre- and post-treatment samples for the carcinoma group.

### 2017-04-21 submission/manuscript.tex

**Figure 1: General Differences between Adenoma, Advanced Adenoma, and
Carcinoma Groups After Treatment.*. A) A significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
NULL). Solid black points represent the median value for each diagnosis
group. B) NMDS of the pre- and post-treatment samples for the adenoma
group. C) NMDS of the pre- and post-treatment samples for the advanced
adenoma group. D) NMDS of the pre- and post-treatment samples for the
carcinoma group.

>>>>

\textbf{Figure 1: General Differences between Adenoma, Advanced Adenoma,
and Carcinoma Groups After Treatment.} A) A significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
NULL). Solid black points represent the median value for each diagnosis
group. B) NMDS of the pre- and post-treatment samples for the adenoma
group. C) NMDS of the pre- and post-treatment samples for the advanced
adenoma group. D) NMDS of the pre- and post-treatment samples for the
carcinoma group.
